\assignment

### 2017-03-19 project/paper.rnw
Almost ready to start fitting models.

easy site, realization 2,000, 390 ft spacing, 6 ft width

>>>>

I simulate data collection along parallel straight-line transects spaced 390
feet apart using a detector with a footprint six feet wide. The location of
the first transect was selected randomly, and all anomalies within three feet
of a transect are observed~(Figure~\ref{fig:sim2000obs}).

<<sim2000obs>>=
# Load the sample data used in my writing project.
ex_anom <- read.anomaly(file.path(vspuxo, 'datasets', 'easy', 'sample',
                        'easy_sample_tTA2_p100_bg100_fg200_rep2000.anomaly'))
ex_path <- read.anomaly(file.path(vspuxo, 'datasets', 'easy', 'sample',
                        'easy_sample_tTA2_p100_bg100_fg200_rep2000.cog'))

par(mar = c(0, 0, 1, 0))
plot(sitewindow, main = 'Observed Geomagnetic Anomalies')
points(y ~ x, data = ex_anom, pch = '.')
@
